An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
Methodology is finished git push

The next step is representing the binary matrix shown in (\ref{eq:lzm_binary}) with histograms. Using the binary values for the overall image representation is not a practical solution. Describing binary data with histograms are more common solution to obtain the image representation. As the methodology described so far, $k^2\times 2K(n)$-sized binary matrix is extracted. Each row of this matrix is linearly combined by weighting each of them as a power of $2$. Hence the final feature vector $\mathbf{X}$ is obtained as follows:

\begin{equation}
\mathbf{X} = 
  \begin{bmatrix}
sgn(a_{00}^{11}) & sgn(b_{00}^{11}) & \hdots & sgn(a_{nm}^{11}) & sgn(b_{nm}^{11}) \\
  \vdots  & \vdots & & \vdots  & \vdots\\
sgn(a_{00}^{1Q}) & sgn(b_{00}^{1Q}) & \hdots & sgn(a_{nm}^{1Q}) & sgn(b_{nm}^{1Q}) \\
  \vdots  & \vdots & & \vdots  & \vdots\\
sgn(a_{00}^{P1}) & sgn(b_{00}^{P1}) & \hdots & sgn(a_{nm}^{P1}) & sgn(b_{nm}^{P1}) \\
  \vdots  & \vdots & & \vdots  & \vdots\\
sgn(a_{00}^{PQ}) &sgn(b_{00}^{PQ}) & \hdots & sgn(a_{nm}^{PQ}) & sgn(b_{nm}^{PQ}) \\
 \end{bmatrix}
 \begin{bmatrix}
2^0 \\
2^1 \\
 \vdots \\
  \vdots \\
   \vdots \\
 2^{2 K(n)-2} \\
 2^{2 K(n)-1}
 \end{bmatrix}=
 \begin{bmatrix}
 x_{11} \\
 \vdots \\
 x_{1Q} \\
  \vdots \\
 x_{P1} \\
  \vdots \\
 x_{PQ} \\
 \end{bmatrix}
 \label{eq:lzm_coded}
\end{equation}
where $x_{i}$ is an integer ranging between $0$ and $2^{2K(n)-1}-1$.

Finally, the input image $I_{p\times q}$ is described with a histogram of length of $2^{2K(n)-1}$.

>>>>

The next step is representing the binary matrix shown in (\ref{eq:lzm_binary}) with histograms. Using the binary values for the overall image representation is not a practical solution. Describing binary data with histograms are more common solution to obtain the image representation. As the methodology described so far, $k^2\times 2K(n)$-sized binary matrix is extracted. Each row of this matrix is linearly combined by weighting each of them as a power of $2$. Hence a column vector $\mathbf{C}$ is obtained with integer values ranging between $0$ and $2^{2K(n)-1}-1$:

\begin{equation}
\mathbf{C} = 
\begin{bmatrix}
c_{j}
\end{bmatrix}=
  \begin{bmatrix}
sgn(a_{00}^{11}) & sgn(b_{00}^{11}) & \hdots & sgn(a_{nm}^{11}) & sgn(b_{nm}^{11}) \\
  \vdots  & \vdots & & \vdots  & \vdots\\
sgn(a_{00}^{1Q}) & sgn(b_{00}^{1Q}) & \hdots & sgn(a_{nm}^{1Q}) & sgn(b_{nm}^{1Q}) \\
  \vdots  & \vdots & & \vdots  & \vdots\\
sgn(a_{00}^{P1}) & sgn(b_{00}^{P1}) & \hdots & sgn(a_{nm}^{P1}) & sgn(b_{nm}^{P1}) \\
  \vdots  & \vdots & & \vdots  & \vdots\\
sgn(a_{00}^{PQ}) &sgn(b_{00}^{PQ}) & \hdots & sgn(a_{nm}^{PQ}) & sgn(b_{nm}^{PQ}) \\
 \end{bmatrix}
 \begin{bmatrix}
2^0 \\
2^1 \\
 \vdots \\
  \vdots \\
   \vdots \\
 2^{2 K(n)-2} \\
 2^{2 K(n)-1}
 \end{bmatrix}
 \label{eq:lzm_coded}
\end{equation}

Finally, the histogram is defined that consists of $2^{2K(n)-1}$ bins, and each bin is filled with the number of occurrences of the integers in $\mathbf{C}$. Therefore, the input image $I_{p\times q}$ is described with a histogram of length of $2^{2K(n)-1}$.
